---
title: "Module 1 - Why make your research open? "
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

## Welcome

Welcome this module on making research open. My name is Peter Reimann and I'll be your guide through this topic. 

Best to get started with a short video: 

![](https://www.youtube.com/watch?v=iE7N3jgF4nU)

A great idea, you might say! But what about...and about...? You will have some concerns. 


## Concerns

Open research means in particular open data: 

"Data is open if it can be freely accessed, used, modified and shared by anyone for any purpose - subject only, at most, to requirements to provide attribution and/or share-alike. Specifically, open data is defined by the Open Definition and requires that the data be

A. Legally open: that is, available under an open (data) license that permits anyone freely to access, reuse and redistribute

B. Technically open: that is, that the data be available for no more than the cost of reproduction and in machine-readable and bulk form.” 
[Open Data Handbook](http://opendatahandbook.org/glossary/en/terms/open-data/)

What does machine-readable mean?

![](https://www.youtube.com/watch?v=frPFDAvc15Q)


```{r concerns}
quiz(
  question("What concerns would you have concerning sharing data from your research?",
    answer("What does stop others from plagiarising my data?", correct = TRUE),
    answer("Wouldn't the privacy of my participants be at risk?", correct = TRUE),
    answer("Other concerns", correct = TRUE)
  )
)
```

## What does it take? 

Watch this video and then try to answer the questions below. 

![](https://www.youtube.com/watch?v=3m6p6w8oOw4)

```{r OpenScienceMeans}
quiz(
  question("Open Science means ...", 
           answer("making my publications available via open access"),
           answer("making my results available"),
           answer("making my data available"), 
           answer("making my instruments and research designs available"), 
           answer("making my data analysis process available"), 
           answer("all of the above", correct = TRUE),
           allow_retry = TRUE
  ),
  question_text("What does the 'I' in FAIR principles stand for?" ,
                answer("Interoperable", correct = TRUE),
                answer("interoperable", correct = TRUE),
                trim = TRUE,
                allow_retry = TRUE
                ),
  question_text("Do you remember one of the characteristics of open science that start with an R? (Start with a capital R)", 
           answer("Reproducible", correct = TRUE),
           answer("Relevant", correct = TRUE),
           answer("Reliable", correct = TRUE), 
           answer("Reusable", correct = TRUE),
           trim = TRUE, 
           allow_retry = TRUE
  )
)
```


